%% -*- mode:latex; ispell-dictionary: "svenska" -*-
%% 'hidelinks' removes colored borders around links etc.
\documentclass[hidelinks,11pt]{article}

%% Nowidow's documentation:
%% http://ftp.acc.umu.se/mirror/CTAN/macros/latex/contrib/nowidow/nowidow.pdf
\usepackage[all]{nowidow} % Tries to remove widows

%% Microtype's documentation:
%% http://ftp.acc.umu.se/mirror/CTAN/macros/latex/contrib/microtype/microtype.pdf
\usepackage{microtype} % Improves typography, load after fontpackage is selected

\usepackage[swedish]{babel} % Swedish
%% \usepackage[UKenglish]{babel} % British English
%% \usepackage[USenglish]{babel} % American English

\usepackage{makecell} % https://ctan.org/pkg/makecell -- \makecell{} \thead{} \multirowthead etc
\renewcommand{\theadfont}{\normalsize\sffamily\bfseries}
\renewcommand{\theadalign}{tl}

\newcommand{\texcommand}[2][…]{\texttt{\textbackslash#2\{#1\}}}

\usepackage{su-thesis}

%% Always used
\suset{author}{Zrajm}
\suset{supervisor}{Ingen}
\suset[swedish]{title}{Mall för uppsats vid Stockholms~universitet}
\suset[swedish]{subtitle}{För \LaTeX{} och Overleaf}
\suset[english]{title}{Thesis Template for Stockholm~University}
\suset[english]{subtitle}{For \LaTeX{} and Overleaf}
\suset[swedish]{keywords}{
  Stockholms universitet, uppsatsmall, nybörjarguide till \LaTeX{},
  kandidatuppsats, masteruppsats, uppsatsskrivande
}
\suset[english]{keywords}{
  Stockholm university, thesis template, beginner's guide to \LaTeX{},
  bachelor's thesis, master's thesis, thesis writing
}
\suset[swedish]{abstract}{
  Detta är en introduktion till hur man använder Stockholms universitets
  uppsatsmall för \LaTeX{}. Här går vi igenom fyra saker: (a) Hur Stockholms
  universitets uppsatsmall ser ut. (b) Vilka möjligheter du, som student vid
  Stockholms universitet, har att använda \LaTeX{}. (c) Hur denna
  \LaTeX{}-version av uppsatsmallen används. Och slutligen (d) går vi i grova
  drag igenom strukturen på hur en uppsats på kandidat- eller masternivå brukar
  se ut på Institutionen för lingvistik. Denna text tjänar också som ett
  exempel på en text skriven i \LaTeX{} och är tänkt att kunna användas som
  utgångspunkt vid uppsatsskrivande.
}
\suset[english]{abstract}{
  This is an introduction to Stockholm university's thesis template for
  \LaTeX{}. In this guide we will cover four things: (a) What thesis template
  of Stockholm university looks like. (b) What choices you, as a student at
  Stockholm university, have for running \LaTeX{}. (c) How to use this \LaTeX{}
  version of the template. And, finally, we also cover roughly (d) what the
  expected structure of a bachelor's or master's thesis look like at the
  Department of Linguistics. This text also serve as an example of a text
  written in \LaTeX{} and is intended as a possible starting point when writing
  a thesis.
}

%% Swedish metadata (only used if language is Swedish)
\suset[swedish]{department}{Institutionen för lingvistik} % e.g. ''
\suset[swedish]{thesistype}{Examensarbete X hp/Degree X HE credits} % e.g. 'Examensarbete 15 hp'
\suset[swedish]{course}{Examensämne} % e.g. 'Lingvistik -- kandidatkurs, LIN600'
\suset[swedish]{program}{Kandidatprogrammet i lingvistik 180 hp}
\suset[swedish]{semester}{Vårterminen 2020}

%% English metadata (only used if language is English)
\suset[english]{department}{Department of Linguistics}
\suset[english]{thesistype}{Bachelor's Thesis 15 ECTS credits}
\suset[english]{course}{Thesis Subject} % e.g. 'Linguistics -- Bachelor's Course, LIN600'
\suset[english]{program}{Bachelor's Programme in Linguistics 180 ECTS credits}
\suset[english]{semester}{Spring semester 2020}

%% Hyphenation patterns
\hyphenation{Fo-ne-tik-lab-bet}

%% Remove margin around lists
\usepackage{enumitem}
\setlist{itemsep=0pt}

%% For XeLaTeX logo
\usepackage{metalogo} % https://ctan.org/pkg/metalogo

%% Suppress abstract page.
%\renewcommand{\sumakeabstractpage}{}

\usepackage{tabularx}
\usepackage{longtable}
\usepackage{multicol}

%% Indent the verbatim environment one em.
%% [https://tex.stackexchange.com/a/148448/185988]
\usepackage{verbatim}
\newlength\myverbindent
\setlength\myverbindent{1em} % change this to change indentation
\makeatletter
\def\verbatim@processline{%
  \hspace{\myverbindent}\the\verbatim@line\par}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%% \include{} automatically does leading & trailing \clearpage.
\include{su-thesis-1-utseende}
\include{su-thesis-2-vilken}
\include{su-thesis-3-hur}
\include{su-thesis-4-mallen}
\include{su-thesis-5-uppsatsstruktur}
\include{su-thesis-6-referenser}
%% \begin{appendices}
%% \include{su-thesis-9-bilagor}
%% \end{appendices}
\end{document}

%% [eof]
